---
title: "combined_media"
author: "kai Wang, Shutong Huo, Yuao Yang, Zongchao Liu"
date: "11/15/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readstata13)
library(DataCombine)
library(dplyr)
library(tidyverse)
library(mediation)
```

# Import data

This part followed the previous modifications. To run the codes you have to have `chwmhh18`.

```{r, include=FALSE}
#### read file child-mother-household
origin = read.dta13("./data/chwmhh18.dta")
### clean
chwmhh <- DropNA(origin, Var = "MT1")
table(chwmhh$MT12)
# non-response
chwmhh <- chwmhh[!(chwmhh$MT1=="9") & !(chwmhh$MT2=="9") & !(chwmhh$MT3=="9") & !(chwmhh$MT4=="9") 
                 & !(chwmhh$MT9=="9") & !(chwmhh$MT11=="9") & !(chwmhh$MT12=="9") ,]
table(chwmhh$MT12)
typeof(chwmhh$MT12)
### outcome 
table(chwmhh$stunting)
### exposure
#chwmhh$magazien <- ifelse(chwmhh$MT1 =='0', 0, 1)
#chwmhh$radio <- ifelse(chwmhh$MT2 =='0', 0, 1)
#chwmhh$tele <- ifelse(chwmhh$MT3 =='0', 0, 1)
chwmhh$magazine <- as.integer(chwmhh$MT1)
chwmhh$radio <- as.integer(chwmhh$MT2)
chwmhh$tele <- as.integer(chwmhh$MT3)
chwmhh$computer <- as.integer(chwmhh$MT4)  
chwmhh$internet <- as.integer(chwmhh$MT9)
chwmhh$phone <- as.integer(chwmhh$MT11)
class(chwmhh$radio)
class(chwmhh$welevel1)
class(chwmhh$wealthp)
table(chwmhh$phone)
class(chwmhh$HH6)
class(chwmhh$stunting)
chwmhh$welevel1 <- as.integer(chwmhh$welevel1)
chwmhh$wealthp <- as.integer(chwmhh$wealthp)  
chwmhh$sex <- factor(chwmhh$HL4, ordered=FALSE)
chwmhh$urbanrural <- factor(chwmhh$HH6, ordered=FALSE)
chwmhh$province <- factor(chwmhh$HH7, ordered=FALSE)
chwmhh$age <- as.integer(chwmhh$UB2)
chwmhh$stunting <- factor(chwmhh$stunting, ordered=FALSE)
```

# Combine Media Variables

Combination Rules:

Newly added variables:

- t_1 : magazine

- t_2 : maximum value for the usage of `computer & internet & phone`

- t_3 : maximum value for the usage of `radio & tele`

This combination rule is a simple trial and can be changed later based on other domain knowledge.

```{r}
### UB2年龄 welevel1母亲教育  wealthp家庭财富 HL4性别 HH6城乡 HH7省份
reg_data = chwmhh %>%
  dplyr::select(stunting, magazine, radio, tele, computer, internet, phone, age, welevel1, wealthp, sex, urbanrural, province,WS9,WB4, UB2, MN36,MN39A,MN39C,MN39G,MN39H,MN39I) %>% # 想加变量在这加！
  # combine media⬇
  mutate(t_1 = factor(magazine),
         t_2 = factor(pmax(computer, internet, phone)),
         t_3 = factor(pmax(radio, tele)))
```

# Analysis

- use `reg_data` for future analysis. It has combined `media` usage. 

```{r}
skimr::skim(reg_data)
```

# Try mediation analysis here...

```{r}

```

